\documentclass[a4paper,12pt]{article}

\usepackage[portuges]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{amsmath, amsfonts, amssymb, mathtools}
\usepackage{array}

\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing


%
% Page display
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}

\addtolength{\topmargin}{-1.25in}
\addtolength{\textheight}{1.75in}

%\pagenumbering{gobble}

\begin{document}

\noindent
\begin{minipage}[t]{0.48\textwidth}
	\vspace{0.01in}	{\Huge \textbf{Luan Lima Freitas}}
\end{minipage}  \hfill \begin{minipage}[t]{0.48\textwidth}
	\begin{flushright}
		+55 21 99557-2129 \\
		\href{mailto:luanclimacfreitas@gmail.com}{luanclimacfreitas@gmail.com} \\
		\href{https://github.com/Luan-Lima-Freitas}{github.com/Luan-Lima-Freitas}
	\end{flushright}
\end{minipage} 

\bigskip

\noindent {\Large Education}

\vskip\smallskipamount
\leaders\vrule width \textwidth\vskip0.4pt
\vskip\medskipamount
\nointerlineskip

\begin{itemize}
	\item \textbf{Federal University of Rio de Janeiro (UFRJ)} \hfill Graduating in December 2022 \\ \textit{Bachelor in Applied Mathematics}
	
	\small{\textit{\textbf{Relevant Coursework:} Numerical Methods, Linear Algebra, Machine Learning, Calculus of Probabilities, Statistical Inference, Mathematical Modeling, Image Processing, Optimization Methods}}
\end{itemize}

\bigskip

\noindent {\Large Skills}

\vskip\smallskipamount
\leaders\vrule width \textwidth\vskip0.4pt
\vskip\medskipamount
\nointerlineskip

\begin{itemize}
	\item \textbf{Programming:} C/C++, Python, Julia
	\item \textbf{Frameworks:} Numpy, Matplotlib, Cvxpy, DiffEqFlux.jl
	\item \textbf{Other Tools:} Git, Google Colab, Jupyter Notebook, \LaTeX
	\item \textbf{Languages:} Native Portugese, Fluent English, Intermediate Spanish, Beginner Mandarin
\end{itemize}

\bigskip

\noindent {\Large Projects and Activities}

%\vskip\smallskipamount
\leaders\vrule width \textwidth\vskip0.4pt
\vskip\medskipamount
\nointerlineskip

\begin{itemize}
	\item \textbf{Undergraduate Research Project} \hfill May 2018 - December 2019 \\
	{\small Research project on animal movement simulation and genetic algorithms. A mathematical model was developed where sensory input would go through a neural network to produce changes in the animal's direction and velocity of movement. The neural network's parameters were then optimized using a genectic algorithm programed in C++.}
	\item \textbf{Undergraduate Research Project} \hfill November 2021 - Present \\
	{\small Research project on modeling and forecasting of epidemiological data using Universal Differential Equations. An UDE consistis of a mathematical model where an explicit term is substituted by a neural network. Modeling and forecasting of COVID-19 data from Rio de Janeiro was developed in Julia's Scientific Machine Learning framework DiffEqFlux.jl.}
	\item \textbf{Tutoring for Scientific Computing Course} \hfill March 2020 - October 2021 \\
	{\small Provided assistance for the students and developed assignments for the Scientific Computing Course at UFRJ.}
\end{itemize}

\noindent {\Large Awards}

\vskip\smallskipamount
\leaders\vrule width \textwidth\vskip0.4pt
\vskip\medskipamount
\nointerlineskip

\begin{itemize}
	\item \textbf{Gold Medal for seven consecutive years at the Brazilian Mathematics Olympiad of Public Schools (OBMEP)} - 2010, 2011, 2012, 2013, 2014, 2015 and 2016.
	\item \textbf{Silver Medal at 2013's Brazilian Mathematics Olympiad (OBM)}
	\item \textbf{Honourable Mention at 2014's Brazilian Mathematics Olympiad (OBM)}
\end{itemize}

\bigskip

\noindent {\Large Interests}

\vskip\smallskipamount
\leaders\vrule width \textwidth\vskip0.4pt
\vskip\medskipamount
\nointerlineskip

I am primarily interested in using technology (in particular machine learning) to develop products which will improve people's quality of life. I am also greatly interested in the scientific and ethical implications of the evolution of artificial intelligence.

\end{document}